Crop adaptation with gene flow from wild relatives

### 2015-09-29 Li_outline.tex

Even though introgression from \emph{mexicana} to Mexican highland maize has been highly supported \cite{hufford2013}, it is yet unknown whether and to what extent such introgression could be found in other highland maize populations, which are allopatric to \emph{mexicana}. 
A recent study \cite{Takuno2015} found little empirical and theoretical support for parallel highland adaptation in the Mexican and South American highland regions, which was explained partly owing to the difference in the potential for adaptive introgression from wild relatives.
Adaptive SNPs in Mexican highland population were more likely located in the introgressed regions than those in South American highland populations.
Furthermore, the adaptive SNPs in Mexican highland population were more likely also showing signatures of local adaptation in \emph{mexicana} and \emph {pulviglumis} populations than those South American highland population.
To sum up, the adaptive introgression from wild relatives may play a significant role in patterning the genetic differences of maize highland populations.
A recent study \cite{Wang2015manuscript} revealed that gene flow exist from \emph{mexicana} not only to Mexican highland maize, but also to Guatamalan highland maize, as well as to some individuals in Southwestern US Highland and even Andes, suggesting different extent contributions \emph{mexicana} made to multiple maize highland landrace populations depending on the distance away from the distribution of \emph{mexicana}. 
However, whether the introgression from \emph{mexicana} to those highland populations contributes to the highland adaptation is awaiting for future research.

>>>>

Even though introgression from \emph{mexicana} to Mexican highland maize has been highly supported \cite{hufford2013}, it is yet unknown whether and to what extent such introgression could be found in other highland maize populations, which are allopatric to \emph{mexicana}. 
A recent study \cite{Takuno2015} found little empirical and theoretical support for parallel highland adaptation in the Mexican and South American highland regions, which was explained partly owing to the difference in the potential for adaptive introgression from wild relatives.
Adaptive SNPs in Mexican highland population were more likely located in the introgressed regions than those in South American highland populations.
Furthermore, the adaptive SNPs in Mexican highland population were more likely also showing signatures of local adaptation in \emph{mexicana} and \emph {pulviglumis} populations than those South American highland population.
To sum up, the adaptive introgression from wild relatives may play a significant role in patterning the genetic differences of maize highland populations.

A recent study \cite{Wang2015manuscript} revealed that gene flow exist from \emph{mexicana} not only to Mexican highland maize, but also to Guatamalan highland maize, as well as to some individuals in Southwestern US Highland, suggesting different extent contributions \emph{mexicana} made to multiple maize highland landrace populations depending on the distance away from the distribution of \emph{mexicana}. 
The Andean maize, the population totally isolated from the occurrence of any teosinte species, underwent the severest historical bottleneck, as a population in the front wave of the serial founder effects. 
The stronger genetic drift introduced by the smaller historical population size improved the homozygosity but reduced the heterozygosity of the population, and it also extended the length of homozygosity.
The high frequency of deleterious alleles caused by stronger genetic drift in the Andes population, together with the reduced efficiency of selection against deleterious sites, contributes to the observed higher mutation load in the well-isolated maize population. 
Even though it is clear that the absence of introgression from wild relatives provided less genetic resource for the highland adaptation and thus made the highland adaptation unique in the Andes, it is yet unknown that out of reach of wild relatives is a reason for reduced fitness in the Andes population.
And the question whether convergent evolution occurs between populations with and without introgression from wild relatives is a key topic for future studies in maize.
